`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`

### 2025-07-10 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/reference-aggregation.Rmd
move jaccard-utils.R into scripts. update docs and path in notebooks to match

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
results_dir <- file.path(module_dir, "results", "singler")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
```

@@

```{r file paths}
# SingleR results
aggr_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "aggregated",
  glue::glue("{params$library_id}_singler-results.rds")
)

non_aggr_singler_file <- file.path(
  results_dir,
  params$sample_id,
  "not-aggregated",
  glue::glue("{params$library_id}_singler-results.rds")
)

@@

```{r}
# Source Jaccard and heatmap utilities functions:
source(file.path(module_dir, "exploratory-notebooks", "jaccard-utils.R"))

>>>>

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
results_dir <- file.path(module_dir, "results")
aggr_results_dir <- file.path(results_dir, "singler-test_aggregated")
non_aggr_results_dir <- file.path(results_dir, "singler-test_not-aggregated")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
```

@@

```{r file paths}
# SingleR results
aggr_singler_file <- file.path(
  aggr_results_dir,
  params$sample_id,
  glue::glue("{params$library_id}_singler-results.rds")
)

non_aggr_singler_file <- file.path(
  non_aggr_results_dir,
  params$sample_id,
  glue::glue("{params$library_id}_singler-results.rds")
)

@@

```{r}
# Source Jaccard and heatmap utilities functions:
source(file.path(module_dir, "scripts", "utils", "jaccard-utils.R"))
